\LARGE \bf An Algorithm to Reduce a Supervisor Demonstrations for DAgger in Learning From Demonstrations[v9]

### 2015-07-28 paper.tex
modified a few comments

Given a candidate policy $\theta$, we can use the surrogate loss function to compute how "close" it is to the competent controller's policy $\tilde{\pi}$.

@@

The optimization problem in Eq. \ref{eq:LFD_obj} compares the action taken of the policy $\pi_\theta$ and  the competent controller, $\tilde{\pi}$  weighted by the probability of  the state occurring $p(\bx|\theta)$.

@@

 To handle the fact that the competent actor's policy contains noise $\epsilon$, we employ a regularization technique in the optimization. Regularization is a technique to control the smoothness of the function that is fit to the sampled data. It is a common technique to make the estimator robust to zero mean noise on data. In practice it is a penalty term on either  the L2 norm on the weights for regression based techniques or the slack coefficient for support vector machines \cite{scholkopf2002learning}.

 \subsubsection{Step 2}
DAgger rolls out the policy $\pi_{\theta_{k=1}}$ to sample states that are likely to occur under $\theta_{k=1}$. For every state visited, DAgger requests the competent controller to provide the appropriate control/label. Formally, for a given sampled trajectory  $\tau = (\bx_1,\bu_1,...,\bx_T\bu_T )$. The competent controller provides labels $\tilde{\bu}_t$, where $\bu_t \sim \pi(\bx_t) + \epsilon$ to the trajectory $\tau = (\bx_1,\tilde{\bu}_1,...,\bx_T, \tilde{\bu}_T )$.  This can be very tedious for a human. The states and labeled controls are then aggregated into the next data set of demonstrations $\mathcal{D}_1$.

@@

Dagger works well in both simulation and real world experiments. It also has theoretical guarantees that it will converge in the limit to the competent controller's policy. However, using policy rollouts means the robot can enter dangerous states, which could damage a robot in a non simulation system. For example, when DAgger was used on a quad-copter the robot repeatedly crashed into trees before successfully learning to avoid them \cite{ross2013learning}. A state can be risky for 2 reasons: 1) its is far from the states trained on, which potentially means our policy will mis-predict the supervisor and incur high surrogate loss \cite{tokdar2010importance} 2) the surrogate loss associated with the state is high, so the state, although visited, doesn't have good control yet. Furthermore, iterations are tedious because if a human is the supervisor requires manual "labeling" of every state visited with the appropriate control.

@@

\vspace{-2ex}
\begin{align}\label{eq:primal_sup}
\underset{w\in F, \mathbf{\xi} \in \mR, \rho \in \mR}{\mbox{min}}\: \frac{1}{2}||w||^2+\frac{1}{vn} \sum^n_i \xi_i - \rho\\
\mbox{s.t} \: \langle w,\Phi(x_i) \rangle \geq \rho - \xi_i, \: \xi_i \geq 0 \\
\end{align}

@@

Estimating the level set of a distribution can be a measure of the generalization ability of $\pi_{\theta}$ to points not within $\mathcal{D}$. However, it does not account for the fact that for a given $\theta$ or  solution to Eq. \ref{eq:super_objj}. $\pi_\theta$ may not correctly match the competent controller's controls for all points train on. To account for this, we propose a modification to the One Class SVM denote:

@@

or $y_i$ is $1$ if the control applied matches the competent controller and $-1$ if it differs. In the regression case the decision between $1$ and $-1$ can be set by a some threshold on a L2-norm or $||\pi_{\theta}(\bx_i)-\bu_i||$. We use $y_i$ to modify the optimization as follows:

@@

Our proposed method trains a policy, $\pi_{\theta_k}$, but also estimates where the policy is likely to accurately predict the competent controller's control,which we define as the region of low risk.  In the statistics community, a known property is that estimators are function will likely mis-classify if they are evaluated at points not in the distribution sampled from.Techniques such as importance sampling use this results to train estimators on data drawn from a different distribution \cite{tokdar2010importance}.  Thus, we try to estimate the level set of the training distribution, which is explained in \ref{sec:level} and only have the competent controller provide labels when the robot leaves this boundary. Furthermore to avoid entering pathological states that are far from the competent controller's demonstrations, we terminate the roll-out when it is a certain distance or risk factor from the decision boundary, which is given by $r(\bx) = \sum_i^n \alpha_i \bx_i k(\bx_i,\bx)-\rho$. The risk threshold, $r_0$, is user defined based on the task.

@@

 \subsubsection{Step 2}
 In DAgger the policy that was rolled out is $\pi_{\theta_k}$, however this could potential encounter pathological states that are far from the initial set of demonstrations $\mathcal{D}_0$. To prevent this we terminate the rolled out policy if the risk, or distance from the support, is above some threshold $r(\bx_t) > r_0$.  Furthermore, instead of labeling every state now the competent controller is only require to label states outside of the level set or $\bx$, where $g(\bx) = -1$.  These states are then added to the dataset $\mathcal{D}_{k+1}$ and the algorithm goes back to Step 1.

@@

\caption{We compare performance in terms of average distance traveled by Mario per stage before dying, running out of time or completing the stage, on randomly generated stages of difficulty 1 with a time limit of 35s to complete the stage.  Stages of difficulty 1 are fairly easy for an average human player but contain most types of enemies and gaps, except with fewer enemies and gaps than stages of harder difficulties. We compare performance of our method and DAgger. In Fig. \ref{fig:mario_results}, we report the performance of distance traveled vs. the number of labels provided by the competent controller. Initial results, averaged over 20 levels, suggest SHEATH was able to reach DAgger's peak performance of a distance around 2200 with only 1200 labels, while DAgger required 2800.   \todo{I think these results are promising but want to make clear they are very preliminary and want to run more experiments on Mario and the self driving car to ensure that we can actually do this reliable. Also, the jaggedness is concerning and needs to be looked in to, my intuition is telling me that Mario is just a very chaotic environment though. I am going to average over more levels to see if it improves}}
\label{fig:mario_results}
\end{figure}

>>>>

Given a candidate policy $\theta$, we can use the surrogate loss function to compute how "close" it is to the supervisor's policy $\tilde{\pi}$.

@@

The optimization problem in Eq. \ref{eq:LFD_obj} compares the action taken of the policy $\pi_\theta$ and  the supervisor, $\tilde{\pi}$  weighted by the probability of  the state occurring $p(\bx|\theta)$.

@@

 To handle the fact that the supervisor's policy contains noise $\epsilon$, we employ a regularization technique in the optimization. Regularization is a technique to control the smoothness of the function that is fit to the sampled data. It is a common technique to make the estimator robust to zero mean noise on data. In practice it is a penalty term on either  the L2 norm on the weights for regression based techniques or the slack coefficient for support vector machines \cite{scholkopf2002learning}.

 \subsubsection{Step 2}
DAgger rolls out the policy $\pi_{\theta_{k=1}}$ to sample states that are likely to occur under $\theta_{k=1}$. For every state visited, DAgger requests the supervisor to provide the appropriate control/label. Formally, for a given sampled trajectory  $\tau = (\bx_1,\bu_1,...,\bx_T,\bu_T )$. The supervisor provides labels $\tilde{\bu}_t$, where $\bu_t \sim \pi(\bx_t) + \epsilon$ to the trajectory $\tau = (\bx_1,\tilde{\bu}_1,...,\bx_T, \tilde{\bu}_T )$.  This can be very tedious for a human. The states and labeled controls are then aggregated into the next data set of demonstrations $\mathcal{D}_1$.

@@

Dagger works well in both simulation and real world experiments. It also has theoretical guarantees that it will converge in the limit to the supervisor's policy. However, using policy rollouts means the robot can enter dangerous states, which could damage a robot in a non simulation system. For example, when DAgger was used on a quad-copter the robot repeatedly crashed into trees before successfully learning to avoid them \cite{ross2013learning}. A state can be risky for 2 reasons: 1) its is far from the states trained on, which potentially means our policy will mis-predict the supervisor and incur high surrogate loss \cite{tokdar2010importance} 2) the surrogate loss associated with the state is high, so the state, although visited, doesn't have good control yet. Furthermore, iterations are tedious because if a human is the supervisor requires manual "labeling" of every state visited with the appropriate control.

@@

\vspace{-2ex}
\begin{align}\label{eq:primal_sup}
\underset{w\in F, \mathbf{\xi} \in \mR, \rho \in \mR}{\mbox{min}}\: \frac{1}{2}||w||^2+\frac{1}{vn} \sum^n_i \xi_i - \rho\\
\mbox{s.t} \: \langle w,\Phi(x_i) \rangle \geq \rho - \xi_i, \: \xi_i \geq 0 \notag
\end{align}

@@

Estimating the level set of a distribution can be a measure of the generalization ability of $\pi_{\theta}$ to points not within $\mathcal{D}$. However, it does not account for the fact that for a given $\theta$ or  solution to Eq. \ref{eq:super_objj}. $\pi_\theta$ may not correctly match the supervisor's controls for all points train on. To account for this, we propose a modification to the One Class SVM denote:

@@

or $y_i$ is $1$ if the control applied matches the supervisor and $-1$ if it differs. In the regression case the decision between $1$ and $-1$ can be set by a some threshold on a L2-norm or $||\pi_{\theta}(\bx_i)-\bu_i||$. We use $y_i$ to modify the optimization as follows:

@@

Our proposed method trains a policy, $\pi_{\theta_k}$, but also estimates where the policy is likely to accurately predict the supervisor's control,which we define as the region of low risk.  In the statistics community, a known property is that estimators are function will likely mis-classify if they are evaluated at points not in the distribution sampled from.Techniques such as importance sampling use this results to train estimators on data drawn from a different distribution \cite{tokdar2010importance}.  Thus, we try to estimate the level set of the training distribution, which is explained in \ref{sec:level} and only have the supervisor provide labels when the robot leaves this boundary. Furthermore to avoid entering pathological states that are far from the supervisor's demonstrations, we terminate the roll-out when it is a certain distance or risk factor from the decision boundary, which is given by $r(\bx) = \sum_i^n \alpha_i \bx_i k(\bx_i,\bx)-\rho$. The risk threshold, $r_0$, is user defined based on the task.

@@

 \subsubsection{Step 2}
 In DAgger the policy that was rolled out is $\pi_{\theta_k}$, however this could potential encounter pathological states that are far from the initial set of demonstrations $\mathcal{D}_0$. To prevent this we terminate the rolled out policy if the risk, or distance from the support, is above some threshold $r(\bx_t) > r_0$.  Furthermore, instead of labeling every state now the supervisor is only require to label states outside of the level set or $\bx$, where $g(\bx) = -1$.  These states are then added to the dataset $\mathcal{D}_{k+1}$ and the algorithm goes back to Step 1.

@@

\caption{We compare performance in terms of average distance traveled by Mario per stage before dying, running out of time or completing the stage, on randomly generated stages of difficulty 1 with a time limit of 35s to complete the stage.  Stages of difficulty 1 are fairly easy for an average human player but contain most types of enemies and gaps, except with fewer enemies and gaps than stages of harder difficulties. We compare performance of our method and DAgger. In Fig. \ref{fig:mario_results}, we report the performance of distance traveled vs. the number of labels provided by the supervisor. Initial results, averaged over 20 levels, suggest SHEATH was able to reach DAgger's peak performance of a distance around 2200 with only 1200 labels, while DAgger required 2800.   \todo{I think these results are promising but want to make clear they are very preliminary and want to run more experiments on Mario and the self driving car to ensure that we can actually do this reliable. Also, the jaggedness is concerning and needs to be looked in to, my intuition is telling me that Mario is just a very chaotic environment though. I am going to average over more levels to see if it improves}}
\label{fig:mario_results}
\end{figure}
